CF Registry Analysis - ROC

### 2024-09-19 Christine Chan/CF Registry/cf_registry_ROC_analysis.qmd
Update cf_registry_ROC_analysis.qmd

---
title: "CF Registry Analysis - ROC"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    fig-width: 8
    fig-height: 8
    page-layout: full
bibliography: /home/tim/Documents/Miscellaneous/zotero.bib
csl: /home/tim/GitHub/styles/american-medical-association.csl
editor: source
---

```{r setup}
#| include: false
library(tidyverse)
library(gtsummary)
library(gt)
library(pROC)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/tim/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/tim/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
set.seed(1017)
```

@@

@@

```{r}
ggplot(roc_df, aes(x = `OGTT 2-hour`, y = hgba1c)) +
  geom_boxplot() +
  ylab("HbA1c") +
  theme_classic()
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = roc_df)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = roc_df)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = peds_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = peds_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = adult_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = adult_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = white_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = white_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = black_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = black_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = more_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = more_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = other_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = other_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

>>>>

---
title: "CF Registry Analysis - ROC"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    fig-width: 12
    fig-height: 9
    page-layout: full
bibliography: /Users/timvigers/Dropbox/Miscellaneous/zotero.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association.csl
editor: source
---

```{r setup}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(gtsummary)
library(gt)
library(pROC)
library(ggrepel)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/tim/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/tim/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
set.seed(1017)
```

@@

```{r}
# Plotting function
roc_plot <- function(roc_obj) {
  c <- coords(roc_obj, "best")
  plot_df <- coords(roc_obj)
  point_df <- plot_df[plot_df$threshold == as.numeric(c[1]), ]
  c <- round(as.numeric(c), 2)
  point_label <- paste0(
    "Threshold: ", c[1], "\n",
    "Specificity: ", c[2], "\n",
    "Sensitivity: ", c[3]
  )
  p <- ggplot(plot_df, aes(x = specificity, y = sensitivity)) +
    scale_x_reverse() +
    geom_line() +
    geom_point(data = point_df) +
    geom_label_repel(
      data = point_df, aes(label = point_label), nudge_x = 0.25,
      segment.color = "grey50", size = 5
    ) +
    xlab("Specificity") +
    ylab("Sensitivity") +
    theme_bw(base_size = 20)
  return(p)
}
```

@@

```{r}
ggplot(roc_df, aes(x = `OGTT 2-hour`, y = hgba1c)) +
  geom_boxplot() +
  ylab("HbA1c") +
  theme_classic(base_size = 20)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_ngt_agt)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

### By ethnicity

#### Hispanic

```{r}
hispanic_ngt_agt <- ngt_agt %>% filter(Hispanicrace == "Yes")
hispanic_agt_cfrd <- agt_cfrd %>% filter(Hispanicrace == "No")
```

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

#### Non-Hispanic

```{r}
non_hispanic_ngt_agt <-
  ngt_agt %>% filter(Race == "Black or African American")
non_hispanic_agt_cfrd <-
  agt_cfrd %>% filter(Race == "Black or African American")
```

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = non_hispanic_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = non_hispanic_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = roc_df)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = roc_df)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = peds_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = peds_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = adult_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = adult_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = white_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = white_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = black_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = black_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = more_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = more_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = other_roc)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = other_roc)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

### By ethnicity

#### Hispanic

```{r}
hispanic_roc <- roc_df %>% filter(Hispanicrace == "Yes")
```

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = hispanic_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, hispanic_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

#### Non-Hispanic

```{r}
non_hispanic_roc <- roc_df %>% filter(Hispanicrace == "No")
```

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = non_hispanic_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = non_hispanic_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```
